---
title: "615_Midterm_Project"
author: "Laura_Wang"
date: "10/21/2019"
output: ioslides_presentation
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("readxl")
library(tidyverse)
library(GPArotation)
library(psych)
```


## Import Data in TW_Survey

- Read text data
```{r }
tw_text<- read_excel("data/F00007687_WV6_Data_Taiwan_2012_Excel_v20180912_text.xlsx")
```

- Read numeric data
```{r}
tw_num<- read_excel("data/F00007625_WV6_Data_Taiwan_2012_Excel_v20180912_num.xlsx")
```

## Select selected-questions and gender column
- We select the questoions fromNo.5-No.12,No.24,No.62,No.161-No.163,No.306-No.308, 16 questions and one gender indicator column.

```{r,echo =FALSE}
tw_select <- select (tw_num,5:12,24,62,161:163,306:308,309)
```

## Replace column name and Handle wrong data
- 1st Since the column name has space and ":"inside, we first replace them with "_" for better data handling.
- 2nd, Since we found that there are worong data in the questionare, which response with -1 and -2, so we delete the rows with worng responses.

```{r,echo =FALSE}
# column name
tw_select_col <- colnames(tw_select)
tw_select_col_copy <- tw_select_col
# split comlumn name 
tw_select_col_code <- str_split_fixed(tw_select_col_copy , ": ", 2)[,1]

# replace column name make it easy to use in filter function
tw_select_col <- str_replace_all(tw_select_col,": ","_")
tw_select_col <- str_replace_all(tw_select_col," ","_")
colnames(tw_select) <- tw_select_col_code

# summary(tw_select)
# Delect wrong data--- response as -1 or -2
tw_select_clean <- tw_select %>%  filter_all(all_vars(.>0))
# summary tw_select_clean to see if still have invalid data
# summary(tw_select_clean)
```


## Factor analysis for TW_Survey data with the selected questions
```{r, echo =FALSE}
# select data for factor analysis
tw_select_fa <- select(tw_select_clean,1:16)

##Correlation matrix
twMatrix <- cor(tw_select_fa)

## Barlett's test 
# cortest.bartlett(tw_select_fa)
# For these data, Bartlett’s test is highly signicant,therefore factor analysis is appropriate.

det(twMatrix)
# This value is greater than the necessary value of 0.00001. As such, our
# determinant does not seem problematic.

# Parallel Analysis
parallel <- fa.parallel(tw_select_fa,fm='minres',fa='fa')


threefactor <- fa(tw_select_fa,nfactors = 3,rotate = "oblimin",fm="minres")
#print(threefactor)

fourfactor <- fa(tw_select_fa,nfactors = 4,rotate =
                     "oblimin",fm="minres")
#print(fourfactor)
#print(fourfactor$loadings,cutoff = 0.3)


fivefactor <- fa(tw_select_fa,nfactors = 5,rotate =
                     "oblimin",fm="minres")
#print(fivefactor)
#print(fivefactor$loadings,cutoff = 0.3)

# The root mean square of residuals (RMSR) is 0.04. This is acceptable as this value should be closer to 0.
# Next we should check RMSEA (root mean square error of approximation) index. Its value, 0.043 shows
# good model fit as it’s below 0.05. Finally, the Tucker-Lewis Index (TLI) is 0.91 – an acceptable value
# considering it’s over 0.9. 


fa.diagram(fivefactor)

#alpha(x=tw_select_fa,check.keys=TRUE)

```

## Plot
- Example: to see thedifferent gender response to V4-V9-significant of Important_in_life
```{r,echo =FALSE }
tw_select_all <- select(tw_num,5:12,24,62,161:163,306:308,309)

colnames(tw_select_all) <- tw_select_col

# tw_select_all

# colnames(tw_select_all)

##Plot 1 different gender response to V4-V9-significant of Important_in_life

tw_select_all$V240_Sex <- factor(tw_select_all$V240_Sex,levels = c(1,2),labels = c("male","female")) 

testdf <- tw_select_all%>%select(1:4,V240_Sex)%>%
    pivot_longer(cols = 1:4,names_to = "Question",values_to = "answer") %>%
    filter(answer>=0)

ggplot(testdf)+
    aes(x = answer,fill = V240_Sex)+
    geom_bar(position = "dodge")+facet_wrap(as.factor(testdf$Question),ncol = 2)
```


